Figures

### 2019-05-10 figures/06_lulc_buffer_demo.Rmd
explore iws with outsized stream buffer ag

>>>>

```{r buffer-lulc_vs_iws-lulc, echo=FALSE}
dt <- readRDS("../data/dt.rds") %>%
  mutate(diff = stream_cultivated_crops - ag_pct) %>%
  drop_na(diff)

# ggplot(data = dt) + 
#   geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = diff > 0)) + 
#   geom_abline(aes(slope = 1, intercept = 0))
# 
# res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
#                       dplyr::filter(dt, diff > 0)$lagoslakeid)
res_iws  <- query_gis("IWS", "lagoslakeid", dplyr::filter(dt, diff > 3)$lagoslakeid)

# ggplot() + 
#   geom_sf(data = state_sf()) +
#   geom_sf(data = res_pnt)

library(curl)
library(glue)
library(slippymath)
library(raster)
library(rgdal)

get_image <- function(outpath, iws){
  # outpath <- outpaths[1]
  # iws <- res_iws[1,]
  tile_grid <- bbox_to_tile_grid(st_bbox(
    st_transform(iws, 4326)), max_tiles = 15)

  mapbox_query_string <-
    paste0("https://api.mapbox.com/v4/mapbox.satellite/{zoom}/{x}/{y}.jpg90",
           "?access_token=",
           Sys.getenv("MAPBOX_API_KEY"))

  images <- apply(tile_grid$tiles, 1, function(i) {
    url     <- glue(mapbox_query_string, x = i[1], y = i[2], 
                zoom = tile_grid$zoom)
    outfile <- glue("../data/mapbox/{x}_{y}.jpg", x = i[1], y = i[2])
    get_if_not_exists(url, outfile)
    return(outfile)
  })

  raster_out <- compose_tile_grid(tile_grid, images)

  writeRaster(raster_out, outpath, options="INTERLEAVE=BAND")   
  return(raster_out)
}

# lapply iws's
outpaths <- paste0("../data/mapbox/", res_iws$lagoslakeid, ".tif")
images   <- lapply(seq_along(outpaths), function(i) 
  get_if_not_exists(get_image, outpaths[i], raster::raster, iws = res_iws[i,]))

iws_sized <- which(abs(res_iws$IWSAreaHa - median(res_iws$IWSAreaHa)) < 1000)
images_sized <- images[iws_sized]

plotRGB(images_sized[[1]])

res_streams <- lapply(iws_sized, function(x) 
  nhdR::nhd_plus_query(poly = res_iws[x,], dsn = "NHDFlowLine")$sp$NHDFlowLine)

viewRGB(images_sized[[1]]) + mapview(res_streams$sp$NHDFlowLine)

library(tmap)

tm_basemap(leaflet::providers$Stamen.Watercolor) +

  tmap_mode("plot")
tm_basemap(leaflet::providers$Stamen.Terrain) + 
  tm_shape(res_iws[8,]) + tm_fill(alpha = 0) + tm_borders() +
    tm_basemap(server = "OpenTopoMap")

  tm_tiles(paste0("http://services.arcgisonline.com/arcgis/rest/services/Canvas/",
    "World_Light_Gray_Reference/MapServer/tile/{z}/{y}/{x}"), group = "Labels")
